Galaxy Zoo: Classifications for Galaxies in HST Legacy Imaging

### 2014-03-07 writeup/gz_hubble_data.tex
edits to paper

@@

We can't do what we did in Bamford et al. (2009) for the original GZ or Willett et al. (2013) for GZ2 because these both depended on the assumption of no redshift bias. In the GZH samples the redshift range is so large that we expect to find redshift evolution of the types and morphologies of galaxies which are seen.

We also expect to see changes in the apparent morphology of galaxies due to band shifting and surface brightness effects (e.g. see Figure \ref{redshift} which illustrates one possible effect of losing features in spiral galaxies at high redshift). So we need to measure this.

@@

So we made images of the same galaxy at a variety of redshifts using input images from the SDSS (cite the SDSS) and the FERENGI code (cite Ferengi) to produce images from these typical of those observed in the HST surveys.

>>>>

\subsection{User Weighting}

The votes of individual users who classified galaxies in Galaxy Zoo Hubble are combined to make a vote fraction for each question on the classification tree. Users votes are weighted slightly (in a method identical to that described in Willett et al. 2013) such that users who frequently disagree with all other users end up having very low weights. The majority of users have weights very close to 1.0 ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.

@@

Previous version of Galaxy Zoo morphology classifications (Lintott et al. 2011, Willett et al. 2013) were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$. In these cases it could be assumed that there was no real evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was assumed to be due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming etc). So for both previous releases of GZ morphogloies, a correction was provided for redshift dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift. See Bamford et al. (2009) and Willett et al. (2013) for the details.

In the GZH samples the redshift range is so large that we expect to find redshift evolution of the types and morphologies of galaxies which are seen. So the previous methods of correcting for redshift dependent bias will not work. In addition the effects of band shifting will change the images even more across these redshift ranges. Figure \ref{redshift} which illustrates one possible effect of losing features in spiral galaxies at high redshift).

@@

In order to test the effects of redshift we made images of the same galaxy at a variety of redshifts using input images from the SDSS (cite the SDSS) and the FERENGI code (cite Ferengi) to produce images from these typical of those observed in the HST surveys.
